Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
Edit final sample 1

    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
    \mstar{} completeness of our samples. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
    \citealt{Lawrence2007}). 
    Comparing to normal SDSS images, the deeper photometry and better photo-$z$s 
    from \texttt{S82-MGC} make this sample complete to \logms{}$\geq 11.2$ at $z<0.7$ 
    which makes it sufficient to evaluate the completeness of our HSC sample.   
	By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts 
    for our sample, is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey is 80\% complete down to 
    $10^{10.8}$\msun at $z{\sim} 0.3$, but is only 80\% complete to 
    $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
    their Fig.~6).

    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$.  
    Because the \texttt{S82-MGC} uses \cmodel{} magnitudes, in this section we use  
    \mcmodel{} for consistency with the \texttt{S82-MGC} catalog.  
    The \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions as 
    used in this work and we find excellent agreement between HSC \mcmodel{} and 
    the mass derived by \texttt{S82-MGC} which includes NIR data from UKIDSS;

@@

	With  \mstar{} estimates in hand, we now use the \redm{} galaxy cluster catalog to  create a sample of massive central galaxies. The ``central'' galaxy is defined as the galaxy that lives in the 
	center of its own dark matter halo.  
	In contrast, a galaxy in a sub-halo that is orbiting within the virial radius of a 
	more massive halo is referred to as a ``satellite''. 
	%The central galaxy has its unique importance in the study of galaxy evolution and 
	%galaxy-halo coevolution.
	To better understand the connection between the structures of massive 
	galaxies and the assembly history of both their stars and dark matter halos, we wish to focus on central 
	galaxies in this work.

@@

    The robust identification of the central galaxy is not an easy task (e.g. \citealt{Yang2007}). In this paper, we use the \redm{} catalog create a sample of massive central galaxies with minimal contamination from satellite galaxies.
\rachel{What about those that are centrals in massive groups?  Also, the \redm{} catalog is not volume-limited to $z=0.5$, so what are the implications for this work?  It wasn't clear to me if that was part of the incompleteness shown in figure 4 since I was not sure if that was after the final selection or not.}

@@

    We use \texttt{v5.10} of the \redm{} cluster  catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}.

>>>>

    With the help of the Stripe82 Massive Galaxy Catalog (\texttt{S82-MGC},
    \citealt{Bundy2015}
    )\footnote{http://www.ucolick.org/$~$kbundy/massivegalaxies/s82-mgc.html}, 
    we investigate the \mstar{} completeness of our samples. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; 
    \citealt{Lawrence2007}). 
    Comparing to normal SDSS images, the deeper photometry and better photo-$z$s 
    from \texttt{S82-MGC} make this sample complete to \logms{}$\geq 11.2$ at $z<0.7$ 
    which makes it sufficient to evaluate the completeness of our HSC sample.   
	By comparing with the \texttt{S82-MGC} sample (\citealt{Bundy2015}), 
	\citet{Leauthaud2016} have measured the \mstar{} completeness of the combined BOSS 
	and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample, which is the main source of redshifts 
    for our sample, is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey is 80\% complete down to 
    $10^{10.8}$\msun{} at $z{\sim} 0.3$, but is only 80\% complete to 
    $10^{12.0}$\msun{} at $z{\sim} 0.5$ according to \citet{Taylor2011} (e.g.\ 
    their Fig.~6).

    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$.  
    Because the \texttt{S82-MGC} uses \cmodel{} magnitudes, in this section we use  
    \mcmodel{} for consistency with the \texttt{S82-MGC} catalog.  
    The \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions as 
    used in this work and we find excellent agreement between HSC \mcmodel{} and 
    the mass derived by \texttt{S82-MGC} which includes NIR data from UKIDSS.

@@

	With \mstar{} estimates in hand, we now use the \redm{} galaxy cluster catalog to  
	create a sample of massive central galaxies. 
	The ``central'' galaxy is defined as the galaxy that lives in the 
	center of its own dark matter halo.  
	In contrast, a galaxy in a sub-halo that is orbiting within the virial radius of a 
	more massive halo is referred to as a ``satellite''. 
	To better understand the connection between the structures of massive 
	galaxies and the assembly history of both their stars and dark matter halos, we 
	wish to focus on central galaxies in this work.

@@

    The robust identification of the central galaxy is not an easy task (e.g.
    \citealt{Yang2007}). 
    In this paper, we use the \redm{} catalog create a sample of massive central 
    galaxies with minimal contamination from satellite galaxies.

@@

    We use \texttt{v5.10} of the \redm{} cluster  catalog
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}.
